figures and calculations for global fisheries management

### 2019-01-12 documents/figs-and-calcs.Rmd
finished basic figures 1,2,3 in documents/figures folder

fig_1 = mtcars %>% 
  ggplot(aes(mpg)) + 
  geom_histogram()

ggsave(here("figures","figure-1.pdf"), fig_1)

@@

projection_data_fig1$CatchShare <- as.factor(projection_data_fig1$CatchShare)

fig_1 = projection_data_fig1 %>%
  ggplot(aes(BvBmsy, FvFmsy, colour = CatchShare, size =MSY, alpha = MSY )) + 
  geom_point() + 
  coord_cartesian(xlim = c(0,3), ylim = c(0,4))+

@@

@@

colnames(projection_data_fig2) <- c("CNTRY_NAME","CatchShare")
projection_data_fig2[projection_data_fig2 =="USA"] <- "United States"
projection_data_fig2$CatchShare <- as.factor(projection_data_fig2$CatchShare)

@@

fig_2 = ggplot() +
  geom_sf(data= projection_spatial, aes(fill = CatchShare))

@@

@@

#projection_data_fig3$CatchShare <- as.factor(projection_data_fig3$CatchShare)

@@

fig_3 = projection_data_fig3 %>%
  ggplot(aes(BvBmsy, FvFmsy, colour = CatchShare, size =MSY, alpha = MSY)) + 
  geom_point() + 
  coord_cartesian(xlim = c(0,3), ylim = c(0,4))+
  scale_alpha(range = c(0.5, 1))+
  theme_minimal() +
  geom_hline(aes(yintercept=1))+
  geom_vline(aes(xintercept=1))+
  xlab("B/Bmsy")+
  ylab("F/Fmsy") +
  ggtitle("Figure 3")

@@

@@

@@

#EDF TURF data
edf_turf <- read_excel("data/EDF_TURF_data.xlsx") %>%
  select("Country", "SciName","CatchShare") %>%
  filter(SciName != "NA")

#DiscoverTURFs data
d_turfs <- read_excel("data/DiscoverTURFs_simple.xlsx") %>%
  select("Country", "SciName", "CatchShare") %>%
  filter(SciName != "NA")

#ISSCAAP Codes
isscaap <- read_csv("data/meta_isscaap_codes.csv")
#######################################################

@@

#question here, will the filter remove out when year is NA? the turf data doesn't have this resolution; edf does have start date though
join_mutate <- left_join(projection_turfs_mutate, gdp, by = "Country") %>% 
  filter(Year == max(Year))

>>>>

@@

projection_data_fig1$Dbase[projection_data_fig1$Dbase == "RAM"]<- "Stock Assessed"
projection_data_fig1$Dbase[projection_data_fig1$Dbase == "FAO"]<- "Stock Not Assessed"

assessed <- projection_data_fig1%>% filter(Dbase == "Stock Assessed")
notassessed <- projection_data_fig1 %>% filter(Dbase == "Stock Not Assessed")

fig_1 = projection_data_fig1 %>%
  ggplot(aes(BvBmsy, FvFmsy, colour = Dbase, size =MSY, alpha = MSY)) + 
  geom_point() + 
  coord_cartesian(xlim = c(0,3), ylim = c(0,4))+
  scale_alpha(range = c(0.5, 1))+
  theme_minimal() +
  geom_hline(aes(yintercept=1))+
  geom_vline(aes(xintercept=1))+
  xlab("B/Bmsy")+
  ylab("F/Fmsy") +
  ggtitle("Figure 1")+
  geom_point(data= assessed, aes(x=median(BvBmsy),y=median(FvFmsy)),size = 3 ,color= "red", shape = 17) +
  geom_point(data= notassessed, aes(x=median(BvBmsy),y=median(FvFmsy)),size = 3 ,color= "blue", shape = 17)

@@

#ggsave(here("documents/figures","figure-1.pdf"), fig_1)

@@

colnames(projection_data_fig2) <- c("CNTRY_NAME","CatchShare")
projection_data_fig2[projection_data_fig2 =="USA"] <- "United States"
projection_data_fig2[projection_data_fig2 =="Russian Federation"] <- "Russia"
projection_data_fig2$CatchShare <- as.factor(projection_data_fig2$CatchShare)

@@

fig_2 = ggplot() +
  geom_sf(data= projection_spatial, aes(fill = CatchShare)) +
  ggtitle("Figure 2")

@@

#ggsave(here("documents/figures","figure-2.pdf"), fig_2)

@@

@@

rbfm <- projection_data_fig3%>% filter(CatchShare == "RBFM")
no_rbfm <- projection_data_fig3 %>% filter(CatchShare == "No RBFM")

fig_3 = projection_data_fig3 %>%
  ggplot(aes(BvBmsy, FvFmsy, colour = CatchShare, size =MSY, alpha = MSY)) + 
  geom_point() + 
  coord_cartesian(xlim = c(0,3), ylim = c(0,4))+
  scale_alpha(range = c(0.5, 1))+
  theme_minimal() +
  geom_hline(aes(yintercept=1))+
  geom_vline(aes(xintercept=1))+
  xlab("B/Bmsy")+
  ylab("F/Fmsy") +
  ggtitle("Figure 3") +
  geom_point(data= rbfm, aes(x=median(BvBmsy),y=median(FvFmsy)),size = 3 ,color= "red", shape = 17) +
  geom_point(data= no_rbfm, aes(x=median(BvBmsy),y=median(FvFmsy)),size = 3 ,color= "blue", shape = 17)

@@

#ggsave(here("documents/figures","figure-3.pdf"), fig_3)
```

@@

### didn't add turf data here yet because using SpeciesCat seems to not work

@@

#EDF TURF data
edf_turf <- read_excel(here("data/EDF_TURF_data.xlsx"))%>%
  select("Country", "SciName","CatchShare") %>%
  filter(SciName != "NA")

#DiscoverTURFs data
d_turfs <- read_excel(here("data/DiscoverTURFs_simple.xlsx")) %>%
  select("Country", "SciName", "CatchShare") %>%
  filter(SciName != "NA")

#ISSCAAP Codes
isscaap <- read_csv(here("data/meta_isscaap_codes.csv"))
#######################################################

@@

#question here, will the filter remove out when year is NA? the turf data doesn't have this resolution; edf does have start date though
join_mutate <- left_join(projection_turfs_mutate, gdp, by = "Country") %>% 
  group_by(IdOrig) %>%
  dplyr::mutate(max_year = max(Year)) %>% 
  filter(max_year== 2012)
